### 2019-06-28 README.Rmd
a bit out of order

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)

@@

You can download the compendium as a zip from from this URL: </archive/master.zip>

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("/")
```

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/worldheritagewikipedia/master?urlpath=rstudio)

@@

You can download the compendium as a zip from from this URL: <https://github.com/benmarwick/worldheritagewikipedia/archive/master.zip>

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("benmarwick/worldheritagewikipedia")
```
